---
output:
  pdf_document: default
  html_document: default
---
Project

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA, 
                      message = FALSE, warning = FALSE)
```

#### Load packages and data

```{r packages, echo = F}
library(tidyverse)
library(broom)
library(class)
library(infer)
library(lubridate)
library(scales)
data <- read_csv("data.csv")
cases <- read_csv("cases.csv")
```
Y'all, the data file is just called data and cases is cases.

## Matt's stuff

```{r matt}
countries <- c("United States", "China", "Italy")

matt_data <- cases %>% 
  filter(location %in% countries) %>% 
  select(location, date, total_cases, new_cases)

ggplot(matt_data, aes(x = date, y = total_cases, color = location)) +
  geom_line() + 
  labs(y = "Total COVID-19 Cases",
       x = "Date",
       color = "Country",
       title = "Both US and Italy see huge spikes",
       subtitle = "Both countries surpasses China on the same day") +
  scale_y_continuous(breaks=seq(0, 700000, 100000),
                     labels = comma) +
  theme_bw()
```


## Larry's stuff

```{r Filter to 3 countries}
countries <- c("United States", "China", "Italy")

data_use <- data %>% 
  filter(
    CountryName %in% countries
  )
data_use
```

```{r Finding out when these countries closed school & recommended closing}
data_use %>% 
  filter(
    `S1_School closing` == 1
  )

data_use %>%
  filter(
    `S1_School closing` == 2
  )
```

Recommended Closing schools:
USA only one out of them that recommended closing before requiring closing, during 20200303

Required Closing schools:
CHN 20200126 first day
ITA 20200223 first day
USA 20200305 first day

```{r Finding out when these countries closed workplaces & recommended closing}
data_use %>% 
  filter(
    `S2_Workplace closing` == 1
  )

data_use %>%
  filter(
    `S2_Workplace closing` == 2
  )
```

Recommended Closing workplaces:
CHN 20200403 first day

Required Closing workplaces:
CHN 20200126 first day
ITA 20200222 first day
USA 20200319 first day

```{r Filter cases list to 3 countries}
countries <- c("United States", "China", "Italy")

cases_use <- cases %>% 
  filter(
    location %in% countries
  )
cases_use
```

```{r Histogram}
cases_use_new <- cases_use %>% 
  filter(
    date == as.Date("2020-04-18")
  )

ggplot(data = cases_use_new, 
  aes(x = location, y = total_cases, fill = location)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(breaks=seq(0, 700000, 100000)) +
  scale_y_continuous(labels = comma) +
  labs(title = "When did these Countries Stop School/Work?",
       x = "Countries", y = "COVID-19 Cases") +
  theme_bw()
```
abline(h=200, col = "Red", lty = 5) *Add lines later on.


## Marcus's Stuff

```{r public-info}
data1 <- data %>%
  filter(CountryName == "Taiwan" | CountryName ==  "South Korea") %>%
  select(CountryName, Date, `S5_Public information campaigns`, `S6_Restrictions on internal movement`,`S7_International travel controls`)

pubinfo <- data1 %>%
  filter(`S5_Public information campaigns` == 1) %>%
  select(CountryName, Date, `S5_Public information campaigns`) %>%
  group_by(CountryName) %>%
  slice(1)
pubinfo

recrestrict <- data1 %>%
  filter(`S6_Restrictions on internal movement` == 1) %>%
  select(CountryName, Date, `S6_Restrictions on internal movement`) %>%
  group_by(CountryName) %>%
  
  slice(1)
recrestrict

restrict <- data1 %>%
  filter(`S6_Restrictions on internal movement` == 2) %>%
  group_by(CountryName) %>%
  select(CountryName, Date, `S6_Restrictions on internal movement`) %>%
  slice(1)
restrict

travelscreening <- data1 %>%
  filter(`S7_International travel controls` == 1) %>%
  group_by(CountryName) %>%
  select(CountryName, Date, `S7_International travel controls`) %>%
  slice(1)
travelscreening

highriskquarantine <- data1 %>%
  filter(`S7_International travel controls` == 2) %>%
  group_by(CountryName) %>%
  select(CountryName, Date, `S7_International travel controls`) %>%
  slice(1)
highriskquarantine

highriskban <- data1 %>%
  filter(`S7_International travel controls` == 3) %>%
  group_by(CountryName) %>%
  select(CountryName, Date, `S7_International travel controls`) %>%
  slice(1)
highriskban
```

Public Info Campaign Start Dates. South Korea: 01/20, Taiwan: 01/20
Recommended Movement Restriction. South Korea: 02/23, Taiwan: NA
Restrict Movement. South Korea: 03/21, Taiwan: NA
International Travel Screening. South Korea: NA, Taiwan: 02/07
Quarantine on high-risk regions. South Korea: NA, Taiwan: 02/24
Ban on high-risk regions. South Korea: 02/03, Taiwan: 02/23

## Kehan's stuff
```{r}
MONEYS<-data_use %>% 
  group_by(CountryName) %>% 
  filter(`S8_Fiscal measures`>0) %>% 
  summarise(sum(`S8_Fiscal measures`)) 

names(MONEYS)[names(MONEYS) ==  "sum(`S8_Fiscal measures`)"] <- "Total_Fiscal_Measures"

MONEYS
```


```{r}
ggplot(data = MONEYS, 
  aes(x = CountryName, y = Total_Fiscal_Measures, fill = CountryName)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(breaks=seq(0, 700000, 100000)) +
  scale_y_continuous(labels = comma) +
  labs(title = "Total Fiscal Measures",
       x = "Countries", y = "COVID-19 Cases") +
  theme_bw()
```

```{r}
data_use %>% 
  filter(`S8_Fiscal measures`>0) %>% 
  arrange(Date) %>% 
  select(CountryName,`S8_Fiscal measures`,Date)
  
```
I WANT TO MAKE TIME MODEL GIF THING


