Project

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA, 
                      message = FALSE, warning = FALSE)
```

#### Load packages and data

```{r packages, echo = F}
library(tidyverse)
library(broom)
library(class)
library(infer)
data <- read_csv("data.csv")
```
Y'all, the data file is just called data


## Larry's stuff

```{r Filter to 3 countries}
countries <- c("United States", "China", "Italy")

data_use <- data %>% 
  filter(
    CountryName %in% countries
  )
data_use
```

```{r Finding out when these countries closed school & recommended closing}
data_use %>% 
  filter(
    `S1_School closing` == 1
  )

data_use %>%
  filter(
    `S1_School closing` == 2
  )
```

Recommended Closing schools:
USA only one out of them that recommended closing before requiring closing, during 20200303

Required Closing schools:
CHN 20200126 first day
ITA 20200223 first day
USA 20200305 first day

```{r Finding out when these countries closed workplaces & recommended closing}
data_use %>% 
  filter(
    `S2_Workplace closing` == 1
  )

data_use %>%
  filter(
    `S2_Workplace closing` == 2
  )
```

Recommended Closing workplaces:
CHN 20200403 first day

Required Closing workplaces:
CHN 20200126 first day
ITA 20200222 first day
USA 20200319 first day






